---
title: "Week05_homework_mhb"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1: Analyze burial mound health

### Loading packages
```{r loading packages}
pacman::p_load(sf, raster, tidyverse, tmap)
```


## Are robbers megalophobes?
Megalophobia is the fear of large objects, and it is therefore interesting to investigate if this fear is something that robbers suffer from, or if they on the contrary are fascinated by big stuff. This initial analysis will thus see if mound height correlates with it being robbed

```{r loading and preprocessing data}
mounds <- read_csv('data/KAZ_mdata.csv')  # Loading data
mounds <- na.omit(mounds)  # Removing NAs
mounds$Robbed <- as_factor(mounds$Robbed)  # Refactoring 'Robbed' column
```


### Exploring the data
First we need to see how the data looks:
```{r exploring data}
summary(mounds)  # Summary
```
Of interesting things in this data summary we can see that there are approximately an equal number of mounds that was robbed and not robbed. Furthermore the mean height of mounds is 1.761 with the tallest being at 20 and the lowest being at 0. 



### Plotting the data
To get an easy look into the tendency between mound height and it being robbed we can plot a boxplot.
```{r plotting data}
# Calculating correlation
boxplot_robbed <- mounds %>% ggplot(aes(Robbed, Height))+
  geom_boxplot()+
  scale_x_discrete(labels = c("Not Robbed", "Robbed"))  # Changing X-labels
boxplot_robbed  # Plotting

```
It seems that there is a tendency, namely, that robbed mounds are often taller but further statistical analysis is needed.


### Statistical analysis
```{r glm}
summary(glm(Robbed ~ Height, data = mounds, family = binomial))  # Statistical analysis
```
As can be seen the p-value is significant and with β = 0.55 (SE = 0.06), z = 9.32, p < .05, it can be said that robbed mounds are on average 0.55 taller than non-robbed mounds. The results could therefore probably, assumably, indicate that robbers might  not suffer from megalophobia, and instead might be intruiged by big stuff. 

**Robber sees big temple = Robber robs**



## Are robbers lazy?
It is easy to understand and sympathesize with robbers not wanting to climb large mountains or similar obstacles just to get a proper loot. It is therefore interesting to see whether there is a correlation between the elevation of a mound and it being robbed. If so it could indicate that robbers are lazy.

### Preprocessing and visualizing the data
```{r loading, preprocessing and visualizing data}
mounds_shp <- st_read('data/KAZ_mounds.shp')  # Loading shape data
mounds <- left_join(mounds_shp, mounds, by = c('TRAP_Code' = 'MoundID'))  # Joining the data with equal identity columns

aster <- raster('data/Aster.tif')  # Loading raster data
aster <- reclassify(aster, cbind(-Inf, 0, NA), right = FALSE)  # Removing NAs

# Assert identical rasters
mounds_crs <- str_split(crs(mounds), ' ')[[1]][3]
aster_crs <- str_split(crs(aster), ' ')[[1]][3]
identical(mounds_crs, aster_crs)  # TRUE

mounds_area <- crop(aster, st_bbox(mounds))  # Cropping the area of the mounds from the aster raster file

tm_shape(mounds_area)+
	tm_raster(style="cont")+  # Plotting with continous raster
tm_shape(mounds)+ 
	tm_dots()+
	tm_layout(title = 'Elevation of the mounds',
		title.position = c('right', 'bottom'),
		legend.position = c('left', 'bottom'))  # Plotting the mounds and the respective elevations
```
It does not seem that there is much of a difference, but yet again, we will turn to statistical methods.

### Preprocessing data for statistics
```{r data preprocessing}
elevation <- raster::extract(mounds_area, mounds)  # Extracting elevation from the raster data
mounds$Elevation <- elevation  # Creating elevation column
mounds <- na.omit(mounds)  # Removing NAs

```

### Plotting data
```{r plotting elevation data}
boxplot_robbed <- mounds %>% ggplot(aes(Robbed, Elevation))+
  geom_boxplot()+
  scale_x_discrete(labels = c("Not Robbed", "Robbed"))  # Changing X-labels
boxplot_robbed  # Plotting
```
It is not easy to assess the laziness of robbers from this boxplot. But it does seem that the mean elevation is slightly lower on robbed mounds. We will now employ mystical GLM magic to create better inference.

### Statistical analysis
```{r glm elevation}
summary(glm(Robbed ~ Elevation, data = mounds, family = binomial))  # Statistical analysis

```
As can be seen the p-value is significant and with β = -0.006 (SE = 0.002), z = -3.36, p < .05. It can, therefore, possibly be said that robbed mounds are on average located 0.006 (meters?) lower than non robbed taller than non-robbed mounds. The results could therefore probably, assumably, indicate that robbers might be lazy. Question mark?

**Robbers are lazy ass bad people**
