---
title: "W1"
author: "Malte Højmark-Bertelsen"
date: "02/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Packages
```{r}
pacman::p_load(leaflet, htmltools, htmlwidgets, tidyverse)
```


### Read data
```{r}
df <- read_csv("data/RCFeature.csv")

```

### Data cleaning
```{r}
df <- df %>% filter(!is.na(Longitude)) %>% filter(!is.na(Latitude))
```


### Creating basic interactive map with different ESRI provider tiles
```{r}
l_bm <- leaflet() %>%   # assign the base location to an object
  setView(lng = mean(df$Longitude),
          lat = mean(df$Latitude),
          zoom = 15)


esri <- grep("^Esri", providers, value = TRUE)

for (provider in esri) {
  l_bm <- l_bm %>% addProviderTiles(provider, group = provider)
}


bm <- l_bm %>%
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")
bm
```



### Creating interactive map of Blue Mountains with markers
```{r}
bm_no_cluster <- bm %>% 
  addTiles() %>% 
  addMarkers(lng = df$Longitude, 
             lat = df$Latitude,
             popup = paste("Feature ID", df$FeatureID, "<br>",
                           "Feature Type:", df$FeatureType, "<br>",
                           "Description:", df$Description, "<br>"),
             #clusterOptions = markerClusterOptions()
             ) %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")
bm_no_cluster
```


### Creating interactive map of Blue Mountains with markers clustering
```{r}
bm_cluster <- bm %>% 
  addTiles() %>% 
  addMarkers(lng = df$Longitude, 
             lat = df$Latitude,
             popup = paste("Feature ID", df$FeatureID, "<br>",
                           "Feature Type:", df$FeatureType, "<br>",
                           "Description:", df$Description, "<br>"),
             clusterOptions = markerClusterOptions()
             ) %>% 
  addLayersControl(baseGroups = names(esri),
                   options = layersControlOptions(collapsed = FALSE)) %>%
  addMiniMap(tiles = esri[[1]], toggleDisplay = TRUE,
             position = "bottomright") %>%
  addMeasure(
    position = "bottomleft",
    primaryLengthUnit = "meters",
    primaryAreaUnit = "sqmeters",
    activeColor = "#3D535D",
    completedColor = "#7D4479") %>% 
  htmlwidgets::onRender("
                        function(el, x) {
                        var myMap = this;
                        myMap.on('baselayerchange',
                        function (e) {
                        myMap.minimap.changeLayer(L.tileLayer.provider(e.name));
                        })
                        }") %>% 
  addControl("", position = "topright")
bm_cluster
```

### Conclusion
Using the clustering algorithm creates very nice clusters of the geographical points, however, it does not manage to give a precise view of the actual location of the ruins in the Blue Mountains. I do, therefore, not recommend using clustering.

### Writing HTML without clustering
```{r}
saveWidget(bm_no_cluster, "bm.html", selfcontained = TRUE)
```
